---
title: "Show and Tell R"
output: html_document
author: "Jenny Sloane"
date: "June 2, 2020"
---
<h2><span style="color:red">Tip 1: install this handy package that shows you each step of your pipe chain sequence </span></h2><br>
- devtools::install_github("daranzolin/ViewPipeSteps") <br>
- highlight your text and click "Addins" and select View Pipe Chain Steps  
```{r message=FALSE, warning=FALSE} 
library(tidyverse)
library(ViewPipeSteps)

mydat <- diamonds %>%
  as_tibble() %>%
  select(carat, cut, price) %>%
  filter(cut == "Ideal" | cut == "Premium") %>%
  arrange(desc(price))

mydat
```

<h2><span style="color:orange">Tip 2: Command+I to clean up misaligned/messy code </span></h2>
```{r}
mydat_messy <- diamonds %>%
    as_tibble() %>%
          select(carat, cut, price) %>%
      filter(cut == "Ideal" | cut == "Premium") %>%
  arrange(desc(price))
 
mydat_clean <- diamonds %>%
  as_tibble() %>%
  select(carat, cut, price) %>%
  filter(cut == "Ideal" | cut == "Premium") %>%
  arrange(desc(price))
```

<h2><span style="color:green">Tip 3: you can hover over a variable that's already been defined and hold down Command (on mac) and click the variable to get a closer look - same function as View() </span></h2> <br>

<h2><span style="color:blue">Tip 4: you can use the mouse wheel to scroll through open tabs within R studio </h2> </span><br>

<h2><span style="color:purple">Tip 5: you can select text/code within a chunk and click insert R (or Alt+Command+I) and it will move it to it's own new chunk </span></h2> <br>

<h2><span style="color:pink">Tip 6: Command + up in console to navigate history </span></h2>

