---
title: "Descriptive Stats, Tables, & Patchwork Package"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning=FALSE)
```

# Load libraries
```{r}
library(tidyverse)
library(psych)
library(palmerpenguins)
library(janitor)
library(gt)
library(papaja)
library(ggeasy)
library(patchwork)
```

# Descriptive Stats
- example from Brick paper
  - load in data
  - clean names
  - create new variable for demographic analyses
  - `tabyl()` and add % - ?tabyl and scroll all the way down and you'll see examples

  - age: mean, min, max 
  - sex: n and percentage
  - `case_when()` example
```{r}
load(file = "merged.rda")

mydata_raw <- merged %>%
  clean_names() %>%
  filter(study == "Prolific")

n_subj = length(unique(mydata_raw$id))

mydata_demo <- mydata_raw %>%
  select(id, age, female) %>%
  na.omit() %>%
  distinct(id, age, female) %>%
  filter(female == 1 | female == 2)

mydata_demo %>%
  summarise(mean_age = mean(age),
            sd_age = sd(age),
            min_age = min(age))

describe(mydata_demo$age) # psych package

# tabyl()
mydata_demo %>%
  tabyl(female) %>%
  adorn_pct_formatting()

range(mydata_demo$age)
# case_when()
data <- mydata_demo %>%
  mutate(age_group = case_when(age < 30 ~ "youngest",
                               age < 55 & age >= 30 ~ "middle",
                               age >= 55 ~ "oldest"))


#cut_number(mydata_demo$age, 3)

mydata_demo %>%
  mutate(gender = case_when(female == 1 ~ "female",
                            female == 2 ~ "male"))

mydata_demo %>%
  mutate(age_group = case_when(age < 50 ~ "younger",
                            age >= 50 ~ "older"))
```


# Formatting Tables

- `gt` package
```{r}
penguins$bill_length_mm <- as.numeric(penguins$bill_depth_mm)

penguins_data <- penguins %>% 
  group_by(species) %>% 
  summarise(mean_bill = mean(bill_length_mm, na.rm = TRUE),
            sd_bill = sd(bill_length_mm, na.rm = TRUE)) 

penguins_data %>%
  gt()  %>%
  fmt_number( # format numbers to 2 decimal places
    columns = c(mean_bill, sd_bill), 
    decimals = 1
  )  %>%
  tab_header( # title and subtitle
    title = "Descriptive Stats",
    subtitle = "Penguin Data"
  ) %>%
  tab_footnote( # you can add 1 or more footnotes
    footnote = "species with bills > 40", 
    locations = cells_body(
      columns = c(mean_bill), 
      rows = mean_bill > 40
    )
  )

```
  
- apa_table() from papaja package
- knit to see table
```{r}
apa_table(penguins_data)
```

# Patchwork Package

Easily plot multiple graphs next to each other
```{r}
my_penguins <- penguins %>%
  na.omit()

plot1 <- ggplot(my_penguins, aes(bill_length_mm, bill_depth_mm)) +
  geom_point() +
  geom_smooth() +
  theme_bw()

plot2 <- ggplot(my_penguins, aes(bill_length_mm, flipper_length_mm)) +
  geom_point() +
  geom_smooth() +
  theme_bw()

plot1 + plot2 
```

